Arbitrary Precision and Arbitrary $n$-grams

### 2011-02-28 paper/paper.Rnw

\begin{figure}
\begin{center}
<<echo=F,fig=T>>=
pp_gen.plot(results.tolstoy)
@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
<<echo=F,fig=T>>=
pp_gen.plot(results.shakespeare)
@
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
<<echo=F,fig=T,height=9>>=
par(mfrow=c(2,1))
pp_gen.plot(results.shakespeare,'Shakespeare')
pp_gen.plot(results.tolstoy,'War and Peace')
@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
<<echo=F,fig=T>>=
#pp_gen.plot(results.shakespeare,'Shakespeare')
@
\end{center}
\end{figure}
